---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# climatevulnerabilitykhm

<!-- badges: start -->

<!-- badges: end -->

## Overview
Data on Effects of Climate Vulnerability on Sanitation Access, Sanitation Infrastructure Functionality and Households’ Fecal Sludge Management Practices in Rural Cambodia.

## Installation

You can install the development version of `climatevulnerabilitykhm` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("openwashdata/climatevulnerabilitykhm")
```

## Data
The package provides access to one dataset.

```{r}
library(climatevulnerabilitykhm)
```

The `climatevulnerabilitykhm` dataset has ? variables and 1472 observations.

## Example
```{r}
library(climatevulnerabilitykhm)
library(ggplot2)
```

```{r}
## basic example code
province <- unique(clmvulnerability$Prov)
cat("The data is collected from the following Cambodian provinces: \n", 
    paste(province, collapse = ", "))
```

### Visualization

Barplot of gender counts
```{r}
ggplot(data = clmvulnerability, aes(Gndr)) +
  geom_bar()
```

Age distribution
```{r}
ggplot(data = clmvulnerability, aes(Age)) +
  geom_histogram(binwidth = 5)
```
